Initial Analysis

### 2020-07-29 Scripts/Initial_Analysis.Rmd
Fixed map labels for tubed map

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             # x =(c(-85.5,-30,25,81,136)+5),
             # y = -93.5,
             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
             y = -9350000,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text", 
             # x =(c(-85.5,-31,20,75,131)+5),
             # y = -110,
             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
             y = -1100000,
             label = Labels, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             # x =-180,
             # y = -93.5,
             x =-18000000,
             y = -9350000,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             # x =-180,
             # y = -110,
             x =-18000000,
             y = -1100000,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      # legend.box.margin = margin(t = -54, l = 130),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area, 
            by = "fishing_entity") %>% 
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_Entity/1000000))
  ) %>% 
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
  group_by(fishing_entity,Variable,Value) %>% 
  summarise(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

>>>>

  ####### For testing ###

  gc()

  plot_all <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0, 0), 
                  y = c(1, 0.45)
  )

  save_plot(
    "Map.png",
    plot_all,
    base_height = 8,
    base_width = 8
  )

  #######

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             # x =(c(-85.5,-30,25,81,136)+5),
             # y = -93.5,
             x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             y = -9050000,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text",
             # x =(c(-85.5,-31,20,75,131)+5),
             # y = -110,
             x =(c(-8500000,-3200000,2000000,7000000,12500000)),
             y = -11000000,
             label = Labels,
             color="black",
             size=3,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             # x =-180,
             # y = -93.5,
             x =-17000000,
             y = -9050000,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             # x =-180,
             # y = -110,
             x =-17000000,
             y = -11000000,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      legend.box.margin = margin(t = -55, l = 120),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area, 
            by = "fishing_entity") %>% 
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_Entity/1000000))
  ) %>% 
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )
